Document Classification

### 2018-10-30 DATA607/Project_4.Rmd
More work on Project 4

## Approach

```{r}
spam_docs <- list.files("data/spam_2")
ham_docs <- list.files("data/easy_ham_2")
```

@@

>>>>

@@

### Train/Test Split

First we are going to split the data into training and testing sets using an 80:20 split.

```{r}
set.seed(12345)
training_percent <- 0.8

train_test_split <- function(data, training_percent){
  n <- round(length(data)*training_percent, digits = 0)
  train <- sort(sample(data, n, replace = FALSE))
  test <- data[!data %in% train]
  return(list(test=test, train=train))
}

spam <- train_test_split(list.files("data/spam_2"), training_percent)
ham <- train_test_split(list.files("data/easy_ham_2"), training_percent)
```

The following table summarizes the number of messages included in each set:

##### Table 1. Spam and Ham Message Counts by Data Set
|      |       Training       |        Testing      |
|------|----------------------|---------------------|
| Spam |`r length(spam$train)`|`r length(spam$test)`|
| Ham  |`r length(ham$train)` |`r length(ham$test)` |

### Pull out Email Contents

This model will classify only on the basis of the content.  The header information will not be taken into consideration.  In order to illustrate the process I will take the first message in the spam training set as an example.

```{r}
example_file <- spam$train[1]

get_email_contents <- function(file_name, path){
 full_path = paste0(path, file_name)
 con <- file(full_path)
 readLines(con)
}

```
